Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-13 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Figure of 10k FE
Randomizer

\begin{itemize}
\item {\em Randomize}
\item {\em Arrays} 
\item {\em Timing functions}
\item {\em Tools} 
\end{itemize}

The performance of the first test is presented in

>>>>

\begin{itemize}
\item {\em Randomize} Both Malab and Java implementations rely on a 
Java Randomizer library as a standardized implementation of the 
randomization of shift vectors and matrices used for the experiments.
The library included the generation of pseudorandom Gaussian of type
double and uniformly distributed integers. Generators used a single
{\tt long} seed. In order to implement the same functionality in
JavaScript, the library random-js was used, as there are inconsistencies 
in the implementation of {\tt Math.random()} between engines in the
number of bits used in the generation and results are non-deterministic. 
The library random-js, implements a Mersenne Twister algorithm producing 
consistent results across all JavaScript implementations assuming the same seed.
\item {\em Arrays} 
\item {\em Timing functions}
\item {\em Tools} 
\end{itemize}

The performance of the time required for 10,000 FEs is presented in Figure \ref{fig:f15_times}.
The test was run on an 3.7 GHz Quad-Core Intel Xeon E5 processor running OS X 10.10.5, 
using Java(TM) SE Runtime Environment (build 1.8.0_25-b17), 
MatLab version R2015a for Mac OSX, Node FrameWork version 0.12.2, Google Chrome Version 46.0.2490.86 (64-bit) 
and Firefox version 41.0.2.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{f15_times.png}
\caption{ Runtime of 10,000 function evaluations (FEs) for $F_{15}$} 
\label{fig:f15_times}
\end{figure}
